DOpElib:\\ Differential Equations and Optimization Environment

### 2013-12-12 Examples/OPT/StatPDE/Example6/content.tex
Doku: Beschreibung der constraints und Rechtschreib-typo im Kommentar des Quellcodes

\subsubsection{Program description}
{
The Problem is similar to that of {\tt OPT/StatPDE/Example1} except for the box control constraints.
The implementation of these constraints is taken care of in the main file
where we add a constrained description \texttt{lcc}.
}

\textcolor{blue}{Winni: Aus den numerischen 
Ergebnissen lese ich ab, das die Kontrolle zwischen 0 und 1 liegt.
\[
0 \leq q \leq 1.
\]
 Aber ich habe keine Ahnung was die Assoziierung zu 
\texttt{
lcc[0][0] = 1; //each component is constrained individualy
  lcc[0][1] = 2; // each two constraints (lower and upper bound)
}
ist. Auch die zugehoerigen Kommentare im main.cc file bringen mich nicht
  wirklich
weiter. Wieso each component? Das ist nur eine Kontrolle?! Oder meint
  component die state-equation component? 
Also konkret: ich kann nicht sagen, wofuer bei \texttt{lcc[0][0] = 1}  die 
einzelnen Eintraege stehen.
}

>>>>

\subsubsection{Program description}

{\textcolor{red}{
The Problem is similar to that of {\tt OPT/StatPDE/Example1} except for the box control constraints.
The implementation of these constraints is taken care of in the main file
(where we add a constrained description \texttt{lcc}) and in the
\texttt{localconstraints.h} file. This files serves to implement the actual constraints. 
In this example, we introduce the handling of \textit{local} constraints
whereas the mixture of local and \textit{global} constraints will be discussed
in the next Example \ref{OPT_Stat_MBB-Beam}. 
%
First, we implement the upper and lower control bounds in 
\texttt{localconstraints.h}, i.e,
\[
q_{min} \leq q \leq q_{max}.
\]
with $q_{min} = -500$ and $q_{max} = 500$.
%
Second, the \texttt{lcc} vector describes the meaning and the applicability of
these constraints. Further information can be found
in \texttt{basic/constraints.h}. We give here the necessary information for
the 
present example. We initialize \texttt{lcc(1)}, i.e., we have 1 control block.
Then, this block is given the constant size $2$ (in the case of more than one 
control block, each block would be given a size of $2$). The first
entry \texttt{lcc[0][\textcolor{red}{0}] = 1} tells 
you how many local entries in the present block are locally constrained, here 
it is $1$ local entry. The second entry \texttt{lcc[0][\textcolor{red}{1}] =
2}, determines the number of constraints on this local entry. Here, we impose 
a lower and an upper bound, i.e., we give 2 constraints.
}

### 2013-12-12 Examples/OPT/StatPDE/Example7/content.tex
Removed Typos in Documentation; OPT/StatPDE/Example1 documentation has been augmented; Introduction has been augmented
Doku: Beschreibung der constraints und Rechtschreib-typo im Kommentar des Quellcodes

This example solves the distributed minimization problem
\begin{gather*}
\min J(q,u) = \frac{1}{2} \|u-u^d\|^2 + \frac{\alpha}{2}\|q\|^2\\
\text{s.t.} (\nabla u,\nabla \phi) = (q+f,\phi)\;\;\forall\,\phi \in H^1_0(\Omega)\\
\text{s.t.} -500 \le q \le 500\;\text{a.e. in }\Omega
\end{gather*}
on the domain $\Omega = [0,1]^2$, and the data is chosen as follows:
\begin{gather*}
 f = \left(20\pi^2  \sin(4 \pi x) - \frac{1}{\alpha}  \sin(\pi x)\right) \sin(2 \pi y)\\
 u^d = \left( 5 \pi^2 \sin(\pi x) + \sin(4 \pi x)\right)  \sin(2\pi y)
\end{gather*}
and $\alpha = 10^{-3}$.

In addition the following functionals are evaluated:
\begin{gather*}
  \text{MidPoint: } u(0.5 ; 0.5)\\[2mm]
  \text{MeanValue: }\int_\Omega u
\end{gather*}

The Problem is similar to that of {\tt OPT/StatPDE/Example1} except for the box control constraints.
Another new feature is the use of the commercial optimization library SNOPT. 
In order to use this library you need to install SNOPT on your computer and then generate a symlink to 
the snopt directory (where you have the libs and the header files) 
in the {\tt DOpE/ThirdPartyLibs} directory named {\tt snopt}, i.e., you should have the file
{\tt DOpE/ThirdPartyLibs/snopt} pointing to the snopt directory. If you have not done this you can compile the
example but when running the example you will only get an error message like\\
{\tt Warning: During execution of `Reduced\underline{ }SnoptAlgorithm::Solve`\\ the following Problem occurred!\\
To use this algorithm you need to have SNOPT installed! \\To use this set the WITH\underline{ }SNOP CompilerFlag.}

>>>>

\subsubsection{General problem description}
This example implements the minimum compliance problem for the thickness optimization 
of an MBB-Beam. Using the MMA-Method of K. Svanberg together with an augmented Lagrangian 
approach for the subproblems following M. Stingl.
%\todo{Gleichung, reference}

The implementation is done using the following three additional files:

\begin{itemize}
\item \texttt{generalized\underline{ }mma\underline{ }algorithm.h}
  An implementation of the MMA-Algorithm for structural optimization using an augmented
  Lagrangian formulation for the subproblems. The subproblem is implemented using the 
  special purpose\\ file \texttt{augmentedlagrangianproblem.h}.
\item \texttt{augmentedlagrangianproblem.h} The problem container 
  for the augmented Lagrangian problem.
\item \texttt{voidreducedproblem.h} A wrapper file that eliminates $u$ 
  if it is not present anyways. This is used so that we can use the same routines to 
  solve problems that have no PDE constraint. This is used to fit the augmentedlagrangian 
  problem into our framework.
\end{itemize}

\subsubsection{Program description}
\textcolor{red}{
In addition to the previous Example \ref{OPT_Stat_MBB-Beam}, we consider now 
in addition 1 global constraint, which is realized by setting $1$ in the 
second argument of \texttt{constraints(lcc, 1)}. 
We use 
\texttt{localconstraints.h} and \texttt{localconstraintaccessor.h} to impose 
all constraints. First, we have again one control block with a lower and 
an upper bound, 
\[
\rho_{min} \leq q \leq \rho_{max}
\]
with $\rho_{min} = 10^{-4}$ and $\rho_{max} = 1$ ($\rho$ denotes the density
of the material). These are implemented in \texttt{localconstraintaccessor.h}.
The global constraint is the maximum volume of the material,
which should remain constant with the value $0.54$. Its implementation is 
provided in \texttt{localconstraints.h}.
}

### 2013-12-12 Examples/OPT/StatPDE/Example8/content.tex
Update Doku. Habe Winnis-Superfunktionen fuer den Moment auskommentiert, da ich trotz tex-Update sonst nicht kompilieren kann
Doku: Beschreibung der constraints und Rechtschreib-typo im Kommentar des Quellcodes

\subsubsection{Program description}
\twick{
The global constraint is inserted in the main file via 
\texttt{constraints(lcc, 1)} instead of 
\texttt{constraints(lcc, 0)} what we had in the previous two examples.
}

>>>>

\subsubsection{Program description}
\textcolor{red}{
In this example, we have now some local (point) constraints, local constraints and a global
constraint. In constrast to the previous example, these 
constraints are all taken care of in the 
\texttt{localconstraints.h} file. 
Specifically, the point constraints are handled by the 
\texttt{DOpE::PointConstraints<...>} function, which is also initializad 
in the main file. 
}
